Improvement of crash forces in structures using optimization tools.

### 2016-07-27 paper.tex
optim strategy 1.0

Once the sampling is obtained, the surrogate model is created. The Multivariate adaptive regression splines (MARS) method is chosen, where the surrogate functions are adjusted with cubic splines following the next expression
\begin{equation}\label{eq:mars}
\hat{f}\left ( \bm{x} \right )= \sum_{m=1}^{M}a_{m}B_{m}\left ( \bm{x} \right ),
\end{equation}
where $B_{m}$ are the power basis functions, $a_{m}$ the coefficients of the functions, and $M$ is the number of functions. This method is more thoroughly explained in \cite{Friedman1995197}.

@@

In the end, the set of points from the Pareto front has a number of components equal to the number of objective functions, each constituting a feasible solution to the problem. This Pareto front points cannot improve the value of one objective function without worsening the value of at least one other objective function.

@@

The methods selected for both the single- and the multi-objective optimization are the genetic algorithms from the JEGA Library, developed by \cite{JEGA}. This methods perform optimization supporting general constraints as well as mixtures of real and discrete variables. The variables are encoded and referred to as chromosomes, and each digit of the variable is a gene.

@@

Before making any calculations with the force-displacement curve, and according to the specialized literature in crash analysis \cite{Huanglibro}, a standard SAE 600 filter \cite{J211} is applied. This removes the high-frequency noise from the curve with a cutoff frequency of ${1000}$ Hz. Once the filter is used, the direct integration of the resulting force-displacement curve yields to the $E_a$:
\begin{equation}\label{Ea}
  E_{a}=\int _{0}^{\delta }F\! \left( z \right) \,dz\,,
\end{equation}
with $\delta$ being the total axial crushing distance and $F\! \left( z \right)$ the value of the crushing force at the crushing length $z$.

@@

The second reason for choosing these objective functions is purely computational. Traditionally, other researchers have swerved towards optimization of the specific energy absorption (SEA) and the load ratio (LR) \cite{Hou2007555}. The SEA function is defined as a ratio between $E_a$ and $m$:
\begin{equation}\label{SEA}
  S\! EA=\dfrac {E_a} {m}
\end{equation}

@@

>>>>

Once the sampling is obtained, the surrogate model is created. The Multivariate adaptive regression splines (MARS) method is chosen, where the surrogate functions are adjusted with cubic splines following the next expression
\begin{equation}\label{eq:mars}
\hat{f}\left ( \bm{x} \right )= \sum_{m=1}^{M}a_{m}B_{m}\left ( \bm{x} \right ),
\end{equation}
where $B_{m}$ are the power basis functions, $a_{m}$ the coefficients of the functions, and $M$ is the number of functions. This method is more thoroughly explained in \citep{Friedman1995197}.

@@

In the end, the set of points from the Pareto front has a number of components equal to the number of objective functions, each constituting a feasible solution to the problem. This Pareto front points cannot improve the value of one objective function without worsening the value of at least one other objective function. \Cref{fig:Pareto} shows an example of a Pareto front opposing the energy absorbed by the specimen and its mass, where the line constitutes the set of optima for these metrics.

\begin{figure}[htpb]
  \centering
   \includegraphics[width=.8\columnwidth]{figures/IMG/Pareto}
  \caption{Pareto frontier opposing energy absorbed and mass of the specimen.}
  \label{fig:Pareto}
\end{figure}

@@

The methods selected for both the single- and the multi-objective optimization are the genetic algorithms from the JEGA Library, developed by \citet{JEGA}. This methods perform optimization supporting general constraints as well as mixtures of real and discrete variables. The variables are encoded and referred to as chromosomes, and each digit of the variable is a gene.

@@

Before making any calculations with the force-displacement curve, and according to the specialized literature in crash analysis \citep{Huanglibro}, a standard SAE 600 filter \cite{J211} is applied. This removes the high-frequency noise from the curve with a cutoff frequency of ${1000}$ Hz. Once the filter is used, the direct integration of the resulting force-displacement curve yields to the $E_a$:
\begin{equation}\label{Ea}
  E_{a}=\int _{0}^{\delta }F\! \left( z \right) \,dz\,,
\end{equation}
with $\delta$ being the total axial crushing distance and $F\! \left( z \right)$ the value of the crushing force at the crushing length $z$.

@@

The second reason for choosing these objective functions is purely computational. Traditionally, other researchers have swerved towards optimization of the specific energy absorption (SEA) and the load ratio (LR) \citep{Hou2007555}. The SEA function is defined as a ratio between $E_a$ and $m$:
\begin{equation}\label{SEA}
  S\! EA=\dfrac {E_a} {m}
\end{equation}

@@

Starting from a baseline model, the optima greatly improve the performance of the model. \Cref{fig:opt_comparison} shows the section of both a baseline model and the single-objective optimum for a maximized SEA.

\begin{figure}[htpb]
\begin{subfigure}[b]{.45\columnwidth}
   \includegraphics[width=\columnwidth]{figures/IMG/sc1.pdf}
    \caption{Baseline model.}
    \label{fig:back0}
\end{subfigure}
\qquad
\begin{subfigure}[b]{.45\columnwidth}
   \includegraphics[width=\columnwidth]{figures/IMG/top_view_foam.eps}
    \caption{Specimen with the optimum SEA value.}
    \label{fig:back5}
\end{subfigure}
\end{figure}
